\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
This diploma thesis presents the design and implementation of the web application \glqq Mediahub\grqq{}, whose purpose is the central management of personal streaming subscriptions with a focus on films. The starting point is the observation that, when several streaming services are used in parallel, users quickly lose track of costs, billing cycles, cancellation dates, and actual film availability. This creates a practical problem that combines organisational and technical aspects.

Within the project, an application was developed collaboratively that combines film information, provider availability, and personal subscription data in a single interface. The work was divided between frontend and backend development. On the frontend side, the implemented functionality includes subscription management, film search, a film detail view, the presentation of matching providers, and protected user areas based on Keycloak. As a result, a functional web application was created that already provides practical value for its users.

At the same time, the thesis shows that developing such an application involves more than implementing isolated features. Key challenges included translating backend data into a clear user interface, integrating authentication, and deliberately limiting the project scope. Not every planned feature was completed in full; for example, the history functionality was only implemented partially. Overall, however, the project provides a technically sound and professionally coherent foundation for future extensions.
